Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-09-23 RR_manuscript/Draft_RR.Rmd
♻️ - update abstract and institutions

---
title: "Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses"
runninghead: "Multidimensional signals and analytic flexibility"
author:
- name: Stefano Coretta*
  num: 1
- name: Joseph V. Casillas
  num: 2
- name: Timo B. Roettger
  num: 3
address:
- num: 1
  org: Institute of Phonetics and Speech Processing, Ludwig-Maximilian University Munich, Germany.
- num: 2
  org: Department of Spanish and Portuguese, Rutgers University, New Brunswick, United States
- num: 3
  org: Department of Linguistics and Scandinavian Studies, University of Oslo, Oslo, Norway
corrauth: "Timo B. Roettger"
email: "timo.b.roettger@iln.uio.no"
abstract: "Recent efforts to replicate published findings have uncovered surprisingly low success rates across disciplines. Moreover, several studies have highlighted the large degree of analytic flexibility in data analysis which can lead to substantially different conclusions based on the same data set. Thus, researchers have expressed their concerns that these researcher degrees of freedom might facilitate bias and can lead to claims that do not stand the test of time. Even greater flexibility is to be expected in fields in which the primary data lend themselves to a variety of possible operationalizations. The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches that derives not only from aspects of statistical modelling but also from decisions regarding the quantification of the measured behavior. In the present study, we will give the same speech production dataset to N teams of researchers and will ask them to answer the same research question. Using Bayesian meta-analytic tools, we will quantify this variability and relate it to predictors related to the analysts and their analyses."
keywords: "crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis"
classoption:
  - Review
  - times
bibliography: references
bibliographystyle: sageh
output:
  bookdown::pdf_book:
    base_format: rticles::sage_article
    keep_tex: yes
    template: template.tex
    includes:
      in_header: preamble.tex
---

>>>>

---
title: "Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses"
runninghead: "Multidimensional signals and analytic flexibility"
author:
- name: Stefano Coretta*
  num: 1, 2
- name: Joseph V. Casillas
  num: 3
- name: Timo B. Roettger
  num: 4
address:
- num: 1
  org: Department of Linguistics and English Language, University of Edinburgh, United Kingdom
- num: 2
  org: Institute of Phonetics and Speech Processing, Ludwig-Maximilian University Munich, Germany
- num: 3
  org: Department of Spanish and Portuguese, Rutgers University, New Brunswick, United States
- num: 4
  org: Department of Linguistics and Scandinavian Studies, University of Oslo, Oslo, Norway
corrauth: "Timo B. Roettger"
email: "timo.b.roettger@iln.uio.no"
abstract: "Recent efforts to replicate published findings have uncovered surprisingly low success rates across disciplines. Moreover, several studies have highlighted the large degree of analytic flexibility in data analysis which can lead to substantially different conclusions based on the same data set. Thus, researchers have expressed their concerns that these researcher degrees of freedom might facilitate bias and can lead to claims that do not stand the test of time. Even greater flexibility is to be expected in fields in which the primary data lend themselves to a variety of possible operationalizations. The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches that derives not only from aspects of statistical modelling but also from decisions regarding the quantification of the measured behavior. In the present study, we gave the same speech production dataset to 30 teams of researchers and asked them to answer the same research question. Using Bayesian meta-analytic tools, we have observed substantial variability between teams and submitted analyses, with analytic and researcher-related predictors having little or no effect on the reported effects."
keywords: "crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis"
classoption:
  - Review
  - times
bibliography: references
bibliographystyle: sageh
output:
  bookdown::pdf_book:
    base_format: rticles::sage_article
    keep_tex: yes
    template: template.tex
    includes:
      in_header: preamble.tex
---

### 2022-09-23 RR_manuscript/Draft_RR.tex
♻️ - update abstract and institutions

\author{Stefano Coretta*\affilnum{1}, Joseph V. Casillas\affilnum{2}, Timo B. Roettger\affilnum{3}}

\affiliation{\affilnum{1}{Institute of Phonetics and Speech Processing, Ludwig-Maximilian University Munich, Germany.}\\\affilnum{2}{Department of Spanish and Portuguese, Rutgers University, New Brunswick, United States}\\\affilnum{3}{Department of Linguistics and Scandinavian Studies, University of Oslo, Oslo, Norway}}

@@

\begin{abstract}
Recent efforts to replicate published findings have uncovered surprisingly low success rates across disciplines. Moreover, several studies have highlighted the large degree of analytic flexibility in data analysis which can lead to substantially different conclusions based on the same data set. Thus, researchers have expressed their concerns that these researcher degrees of freedom might facilitate bias and can lead to claims that do not stand the test of time. Even greater flexibility is to be expected in fields in which the primary data lend themselves to a variety of possible operationalizations. The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches that derives not only from aspects of statistical modelling but also from decisions regarding the quantification of the measured behavior. In the present study, we will give the same speech production dataset to N teams of researchers and will ask them to answer the same research question. Using Bayesian meta-analytic tools, we will quantify this variability and relate it to predictors related to the analysts and their analyses.
\end{abstract}

>>>>

\author{Stefano Coretta*\affilnum{1, 2}, Joseph V. Casillas\affilnum{3}, Timo B. Roettger\affilnum{4}}

\affiliation{\affilnum{1}{Department of Linguistics and English Language, University of Edinburgh, United Kingdom}\\\affilnum{2}{Institute of Phonetics and Speech Processing, Ludwig-Maximilian University Munich, Germany}\\\affilnum{3}{Department of Spanish and Portuguese, Rutgers University, New Brunswick, United States}\\\affilnum{4}{Department of Linguistics and Scandinavian Studies, University of Oslo, Oslo, Norway}}

@@

\begin{abstract}
Recent efforts to replicate published findings have uncovered surprisingly low success rates across disciplines. Moreover, several studies have highlighted the large degree of analytic flexibility in data analysis which can lead to substantially different conclusions based on the same data set. Thus, researchers have expressed their concerns that these researcher degrees of freedom might facilitate bias and can lead to claims that do not stand the test of time. Even greater flexibility is to be expected in fields in which the primary data lend themselves to a variety of possible operationalizations. The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches that derives not only from aspects of statistical modelling but also from decisions regarding the quantification of the measured behavior. In the present study, we gave the same speech production dataset to 30 teams of researchers and asked them to answer the same research question. Using Bayesian meta-analytic tools, we have observed substantial variability between teams and submitted analyses, with analytic and researcher-related predictors having little or no effect on the reported effects.
\end{abstract}
